Graph Topological Aspects of Granger Causal Network Learning

### 2019-07-24 paper/paper.tex
LASSO paragraph.

A second and wildly successful heuristic is the LASSO regularizer
\cite{tibshirani1996regression}, which can be understood as a natural
convex relaxation to penalizing the count of the non-zero edges.  The
LASSO enjoys fairly strong theoretical guarantees
\cite{wainwright2009sharp}, extending largely to the case of
stationary time series data with a sufficiently fast rate of
dependence decay \cite{basu2015} \cite{wong2016lasso}
\cite{autoregressive_process_modelling_via_the_lasso_procedure}, and
variations on the LASSO have been applied in a number of different
time series contexts as well as Granger-causality
\cite{DBLP:journals/corr/HallacPBL17} \cite{haufe2008sparse}
\cite{bolstad2011causal} \cite{he2013stationary}
\cite{grouped_graphical_granger_modelling_for_gene_expression_regulatory_networks_discovery}.
One of the key improvements to the original LASSO algorithm is the
adaptive (i.e. weighted) ``adaLASSO'' \cite{adaptive_lasso_zou2006},
for which oracle results (i.e. asymptotic support recovery) are
established under less restrictive conditions than for the vanilla
LASSO.  Our experimental comparisons in Section
\ref{sec:empirical_evaluation} are against the
adaLASSO. % Success of the LASSO has lead to
% the famous ``bet on sparsity'' principle ``Use a procedure that does
% well in sparse problems, since no procedure does well in dense
% problems.''  \cite{tibshirani2015statistical}.

>>>>

A second and wildly successful heuristic is the LASSO regularizer
\cite{tibshirani1996regression}, which can be understood as a natural
convex relaxation to penalizing the count of the non-zero edges.  The
LASSO enjoys fairly strong theoretical guarantees
\cite{wainwright2009sharp}, extending largely to the case of
stationary time series data with a sufficiently fast rate of
dependence decay \cite{basu2015} \cite{wong2016lasso}
\cite{autoregressive_process_modelling_via_the_lasso_procedure}, and
variations on the LASSO have been applied in a number of different
time series contexts as well as Granger-causality
\cite{DBLP:journals/corr/HallacPBL17} \cite{haufe2008sparse}
\cite{bolstad2011causal} \cite{he2013stationary}
\cite{grouped_graphical_granger_modelling_for_gene_expression_regulatory_networks_discovery}.

The LASSO algorithm is known to suffer from a large proportion of
false-positives (e.g. see \cite{fdr_lasso}), except when certain
stringent conditions are met.  One of the key improvements to the
original LASSO algorithm is the adaptive (i.e. weighted) ``adaLASSO''
\cite{adaptive_lasso_zou2006}, for which oracle results
(i.e. asymptotic support recovery) are established under less
restrictive conditions.  Our experimental comparisons in Section
\ref{sec:empirical_evaluation} are against the
adaLASSO.
